--- 
title: "Sonorezé"
author: "Tristan Lorino"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: sonoreze/WorkinprogReze
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

GitHub Pages va puiser les pages html dans le dossier **/docs**. Pour déployer le *bookdown* sur Github, on ajoute au fichier _bookdown.yml la commande :

```{r eval=FALSE}
output_dir: "docs"
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

```{r,echo=FALSE}
if (!require("pacman")) install.packages("pacman")
library(pacman)
pacman::p_load(here,thematic,lubridate,dplyr,tidyr,stringr,ggplot2,ggforce,forcats,rgdal,sp,sf,
               rgeos,geoR,tidyr,devtools,leaflet,leaflet.extras,jsonlite,RColorBrewer,
               viridis,forcats,mapview,scales,flexdashboard,fontawesome,rprojroot,ggthemes,plotly,spacetime,gstat)
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

On charge les données issues de *metabase* et on indique le dossier de travail :
```{r}
load(here("noisecapture_data.Rda"))
here()
source(here("R","Statistiques.R"))
#source("./Users/tristanlorino/Documents/GitHub/WorkinprogReze/docs/Statistiques.R")

noisecapture_data <- as.data.frame(noisecapture_data)
```
